---
title: "ESM 204 HW 4"
author: "Peter Omasta, Jennifer Truong, and Veronica Weber"
date: "5/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)

# Attach packages
library(tidyverse)
library(janitor)
```

```{r Functions}

# Maybe all of these can become one function later

# Function for finding temperature under BAU ----

# tau(t) = min(Tt/100, T)
bau_temp = function(t, T){
  tau = min((T*t)/100, T)
  return(tau)
}

# Function for fraction of economic activity that is retained ----

# "consumption" = economic activity)

# K(t) = exp(−beta*tau(t)^2)
econ_activity_retained = function(t, beta, tau){
  k_t = exp(-beta*tau)
  return(k_t)
}

# Function for total consumption at time t ----

# C(t) = K(t)exp(gt)
consumption = function(t, k_t, g){
  c_t = k_t*exp(g*t)
  return(c_t)
}


# Function for society's utility ---

# U(C) = (C1−eta)/(1 − eta)
society_utility = function(c_t, eta){
  u_c = (c_t^(1-eta))/(1-eta)
  return(u_c)
}


# Function for discount rate ----

# Discount rate - Ramsey rule
discount_rate = function(delta, eta, g){
  r = delta + eta*g
  return(r)
  }
```

```{r Parameters}

# Setting up vector for time t
year = c(0:200)

# Use the following base case parameters for this model: delta = .005, eta = .5, g = .01, beta = .05.

```

# 1. Plots 

### a) temperature over time

- no climate change (T = 0)
- moderate climate change (T = 2)
- extreme climate change (T = 8)

```{r Finding temperature over time}

# Find BAU temp under T = 0
temp_t_0 = lapply(year, bau_temp, T = 0)

# Find BAU temp under T = 2
temp_t_2 = lapply(year, bau_temp, T = 2)

# Find BAU temp under T = 8
temp_t_8 = lapply(year, bau_temp, T = 8)

# Create data frame
temperature_df = tibble(year, temp_t_0, temp_t_2, temp_t_8) %>% 
  rename("no_cc" = "temp_t_0",
         "moderate_cc" = "temp_t_2",
         "extreme_cc" = "temp_t_8")
```

```{r Plot of temperature vs time}

# Code doesn't work for now - need to figure out what's wrong

ggplot() +
  geom_point(temperature_df,
             aes(x = year, y = no_cc),
             color = "green") +
  geom_point(temperature_df,
             aes(x = year, y = moderate_cc),
             color = "yellow") +
  geom_point(temperature_df,
             aes(x = year, y = extreme_cc),
             color = "red")
```

### b) Consumption over time

- no climate change (T = 0)
- moderate climate change (T = 2)
- extreme climate change (T = 8)

```{r Finding consumption over time}

# Find consumption under T = 0
consumption_t_0 = lapply(year, econ_activity_retained, beta = .05, tau = temp_t_0)

# Find consumption under T = 2
temp_t_2 = lapply(year, bau_temp, T = 2)

# Find consumption under T = 8
temp_t_8 = lapply(year, bau_temp, T = 8)

# Create data frame
temperature_df = tibble(year, temp_t_0, temp_t_2, temp_t_8) %>% 
  rename("no_cc" = "temp_t_0",
         "moderate_cc" = "temp_t_2",
         "extreme_cc" = "temp_t_8")

```

### c) Undiscounted utility over time

# 2. Analysis

### a) Suppose T = 4.4. What is the present value (i.e. discounted) utility over the next 200 years with climate change? What is the present value utility without climate change? What is the percentage loss in present value utility from climate change (call this L)?

In other words, suppose we know for sure that under BAU, climate change will eventually lead to a 4.4 degree increase in temperature.

```{r Find Present Value Utility Under T = 4.4}

# Find BAU temp under T = 4.4 ----

temp_t_44 = lapply(year, bau_temp, T = 4.4)

```


### b) Now show how sensitive your calculation of L is to the following parameters: T, g, eta, and beta. To do so, calculate the % change in L that arises from a 10% increase in each of these parameters.

### c) Back to the original parameters, suppose we could completely prevent climate change from occurring (so T = 0 instead of T = 4.4) but doing so would require giving up a fraction theta of consumption every year for the next 200 years. What is the maximum value of theta society would be willing to endure every year to completely prevent climate change? Call this theta*.

### d) Suppose we are uncertain about T, but it has the following probability distribution: T = 2 (with probability .2), T = 4 (with probability .5), and T = 6 (withprobability .3). Calculate theta* under uncertainty over T.
